What We Eval in the Shadows

### 2021-08-06 paper/main.tex
Improve provenance section

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions, or by building a call with \c{call} or \c{as.call}.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function. Function arguments are passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise. \c{formals} access the argument list of a function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\item {\it Symbols: }   a symbol is created with \c{as.name} or \c{as.symbol}, typically to find the value of a symbol in a non-local environment.
\end{compactitem}

@@

\begin{wraptable}{r}{5cm}\small\centering
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Constructed & \packageNbConstructedSites & \packageNbConstructedSitePercent \\
Reflection &  \packageNbMatchCallExprsSites & \packageMatchCallExprsSitePercent\\
String & \packageNbStringSites & \packageNbStringSitePercent \\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{wraptable}

@@

\paragraph{Discussion}
The origin data suggests that constructing expressions from strings is a
minority of the use cases. Instead, the constructed category shows that most
\evals comes from code that was processed by the compiler, and may be slightly
modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those.

>>>>

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions, or by building a call with \c{call} or \c{as.call}.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function. Function arguments are passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise. \c{formals} access the argument list of a function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\item {\it Environment: }   a symbol is created with \c{as.name} or \c{as.symbol}, typically to find the value of a symbol in a non-local environment.
\end{compactitem}

@@

\begin{wraptable}{r}{5cm}\small\centering
\begin{tabular}{r|r|r} \hline
Origin  & \#sites & \%sites \\\hline
Constructed & \packageNbConstructedSites & \packageConstructedSitesPercent \\
Reflection &  \packageNbReflectionSites & \packageReflectionSitesPercent\\
Environment & \packageNbSymbolSites & \packageSymbolSitesPercent \\
String & \packageNbStringSites & \packageStringSitesPercent \\\hline
\end{tabular}
\caption{Provenance}\label{tab:provenance}
\end{wraptable}

@@

\paragraph{Discussion}
The origin data suggests that constructing expressions from strings is a
minority of the use cases. Instead, the constructed category shows that most
\evals comes from code that was processed by the compiler, and may be slightly
modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those. Another use of \eval is to directly build symbols to evaluate them in another environment than the default one.
